---
title: "Product review: Google Analytics"
author: "Impact team"
date: "`r Sys.Date()`"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
        code_folding: "hide"
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(fuzzyjoin)
library(DT)
# library(kableExtra)
# library(zoo)
library(plotly)
library(reactable)
```

```{r, include = FALSE}
# Specify time period GA data is available for
month_start <- ym("2019-06")
month_end <- ym("2022-06")
```


```{r, include = FALSE}
# Calculate number of months
months_diff <- floor((month_start %--% month_end) / dmonths(1))

# Create vector with all the relevant months
month_list <- month_start + months(0:months_diff)

# Generate file names using months specified above
downloads_filename <- map(month_list, ~ sprintf("./download_analytics/HSC dashboard - Engagement and implementation_All webpages_ links and downloads_Table_%s.csv", as.character(.x) %>% str_remove("-01$")))

views_filename <- map(month_list, ~ sprintf("./download_analytics/HSC dashboard - Engagement and implementation_All webpages_ links and downloads_Table_views_%s.csv", as.character(.x) %>% str_remove("-01$")))
```


```{r, include = FALSE}
# Import data
import_data <- function(filenames) {
    filenames %>%
        set_names() %>%
        map_dfr(read_csv, col_types = "ccd", .id = "filename")
}


downloads_data <- import_data(downloads_filename)

views_data <- import_data(views_filename)

```


```{r, include = FALSE}
# Extract the date from the file name
extract_date <- function(table, date_regex) {
    table %>% 
        mutate(year_month = str_extract(filename, date_regex) %>% ym(.)) %>% 
        select(-filename) %>%
        janitor::clean_names() %>%
        select(year_month, everything())
}

downloads_data <- extract_date(downloads_data, "(?<=Table_)\\d{4}-\\d{2}(?=.csv)")

views_data <- extract_date(views_data, "(?<=Table_views_)\\d{4}-\\d{2}(?=.csv)")

```

```{r, include = FALSE}
# List of products with filename regex
dl_product_list <- list("QSSIT" = "((QS)|(quality-standard))-service-improvement-template",
                      "Baseline assessment tool" = "baseline-assessment-tool",
                      "Resource planner" = "resource-planner",
                     "Resource impact template" = "resource-impact-template",
                     "Resource impact report" = "resource-impact-report"
)

views_product_list <- list("Resource impact report" = "resource-impact-report"
)

```

Downloads


Inputs

```{r, echo = FALSE}
selectInput("dl_select_products", 
                "Select products to view downloads data:",
                choices = dl_product_list,
                multiple = TRUE)
```


```{r, echo = FALSE}
dl_selected <- reactive({
    dl_selected <- downloads_data %>% 
            filter(str_detect(file, regex(str_c(input$dl_select_products, collapse = "|"), ignore_case = TRUE)))
    
    dl_product_list_tbl <- tibble(product = names(dl_product_list), regex = dl_product_list)

    dl_selected %>% 
        regex_inner_join(dl_product_list_tbl,
                         by = c(file = "regex")) %>% 
        select(-regex) %>% 
        mutate(product = as_factor(product))
    })

dl_monthly <- reactive({
    dl_selected() %>% 
        group_by(product, year_month) %>% 
        summarise(monthly_downloads = sum(downloads))
})
```

Row 


### How much are the products being downloaded across all NICE webpages, monthly?

```{r, echo = FALSE}
renderPlotly({
    req(input$dl_select_products)
    
    fig <- ggplot(data = dl_monthly(),
                  aes(x = year_month, y = monthly_downloads, colour = product)) +
        geom_line() +
        labs(x = "Month",
             y = "Downloads") +
        scale_y_continuous(expand = c(0,0),
                           limits = c(0, NA)) +
        scale_x_date(date_breaks = "6 months",
                     date_labels = "%b %Y")


    ggplotly(fig)
})
```

### Table

```{r, echo = FALSE}
renderDT(dl_monthly(),
         filter = "top",
         extensions = c("Scroller", "Buttons"),
         options = list(
             scrollY = 400,
             scrollX = TRUE,
             scroller = TRUE,
             dom = "Bfrtip",
             buttons = c('copy', 'csv', 'excel')
             ),
         rownames = FALSE) 
```

Row 

### Which pages are the products most frequently downloaded from?

All pages contributing less than 5% to the monthly download of a product are collapsed into "Other".

Note, while the QSSIT and resource planner are the same product regardless of which webpage it exists on, the BATs, resource impact templates and resource impact reports are specific to the guideline they belong to.

```{r, include = FALSE}
download_page <- reactive({
    dl_selected() %>%
        group_by(product) %>% 
        mutate(downloaded_from = fct_lump_prop(page_path, w = downloads, prop = 0.05)) %>% 
        ungroup()
})
```

```{r, echo = FALSE}
renderPlotly({
    req(input$dl_select_products)
    
    source_fig <- download_page() %>%
        group_by(product, year_month, downloaded_from) %>%
        summarise(monthly_downloads = sum(downloads)) %>%
        ggplot(aes(x = year_month,
                   y = monthly_downloads, 
                   colour = product, 
                   linetype = downloaded_from)) +
        geom_line() +
        labs(x = "Month",
             y = "Downloads") +
        scale_y_continuous(expand = c(0,0),
                           limits = c(0, NA)) +
        scale_x_date(date_breaks = "6 months",
                     date_labels = "%b %Y")


    ggplotly(source_fig)
})

```

### Table
```{r, echo = FALSE}
renderReactable({
    download_page() %>%
        select(-file) %>% 
        reactable(.,
                  filterable = TRUE,
                  searchable = TRUE,
                  groupBy = c("product", "year_month", "downloaded_from"),
                  columns = list(
                      downloads = colDef(aggregate = "sum")
                      )
                  )
})

```

### Individual pages

```{r, echo = FALSE}
renderPlotly({
    req(input$dl_select_products)
    
    highlight_line <- highlight_key(dl_selected(), ~page_path)
    
    page_line <- highlight_line %>%
        ggplot(aes(x = year_month,
                   y = downloads,
                   group = page_path,
                   colour = product)) +
        geom_line() +
        labs(x = "Month",
             y = "Downloads") +
        scale_y_continuous(expand = c(0,0),
                           limits = c(0, NA)) +
        scale_x_date(date_breaks = "6 months",
                     date_labels = "%b %Y")


    ggplotly(page_line, tool_tip = "page_path") %>% 
        highlight(on = "plotly_hover",
                  off = "plotly_doubleclick",
                  color = "red")
})
```




### Raw downloads data showing page downloaded from and file download URL

```{r, echo = FALSE}
renderDT(dl_selected() %>% select(product, everything()),
         filter = "top",
         extensions = c("Scroller", "Buttons"),
         options = list(
             scrollY = 400,
             scrollX = TRUE,
             scroller = TRUE,
             dom = "Bfrtip",
             buttons = c('copy', 'csv', 'excel')
             ),
         rownames = FALSE) 
```



```{r, echo = FALSE}
selectInput("views_select_products", 
                "Select products to view page views for:",
                choices = views_product_list,
                multiple = TRUE)
```


```{r, echo = FALSE}
views_selected <- reactive({
    views_selected <- views_data %>% 
            filter(str_detect(file, regex(str_c(input$views_select_products, collapse = "|"), ignore_case = TRUE)))
    
    views_product_list_tbl <- tibble(product = names(views_product_list), regex = views_product_list)

    views_selected %>% 
        regex_inner_join(views_product_list_tbl,
                         by = c(file = "regex")) %>% 
        select(-regex) %>% 
        mutate(product = as_factor(product))
    })

views_monthly <- reactive({
    views_selected() %>% 
        group_by(product, year_month) %>% 
        summarise(monthly_downloads = sum(downloads))
})
```
